\textbf{Emergency Service Location Optimization in a Multi-Zone District based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex

\subsection{Zone-to-Zone Population Dynamics}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
zone-to-zone coverage.
\begin{description}
    \item[$A(t), B(t)$] Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$Z_{AB}(t)$] Zone-to-zone coverage of  B from  A
    \item[$v$] required ambulance response time
    \item[$T_{AB}$] travel time from A to B, given
    \item[$T_{BA}$] travel time from B to A, given
    \item[$P_B$] total population of B
    \item[$F_B(s)$] the probability curve for differences in travel time within B
    \item[$T_{A^+}$] travel time inside of A traveling away from B
    \item[$T_{A^-}$] travel time inside of A traveling toward B
    \item[$T_{B^+}$] travel time inside of B traveling away from A
    \item[$T_{B^-}$] travel time inside of B traveling toward A
    \item[$a, b$] width of A and B respectively
    \item[$g$] width of the gap between A and B
\end{description}

%TODO: Graphical representation of origin and setup

The function for zone-to-zone coverage in respect to travel time can be written out as 
$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B. This is the average difference in travel time, and is equal to $T_{B+}$. 
$$T_{B+} = \int^{T_{AB}}_{T_{AB} - b} s F_B(s) ds$$

\subsection{Ambulance Distributor}
Once the zone-to-zone coverages have been

>>>>

\subsection{Part 1?}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
zone-to-zone coverage.
\begin{description}
    \item[$A(t), B(t)$] Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$Z_{AB}(t)$] Zone-to-zone coverage of  B from  A
    \item[$v$] required ambulance response time
    \item[$T_{AB}$] travel time from A to B, given
    \item[$T_{BA}$] travel time from B to A, given
    \item[$P_B$] total population of B
    \item[$T_{A^+}$] travel time inside of A traveling away from B
    \item[$T_{A^-}$] travel time inside of A traveling toward B
    \item[$T_{B^+}$] travel time inside of B traveling away from A
    \item[$T_{B^-}$] travel time inside of B traveling toward A
    \item[$a, b$] width of A and B respectively
    \item[$g$] width of the gap between A and B
\end{description}

%TODO: Graphical representation of origin and setup
The function for zone-to-zone coverage in respect to travel time can be written out as 
$$Z_{AB}(t) = P_B * \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$

\subsection{Ambulance Distributon Optimization}
Once the zone-to-zone coverages have been calculated, we must still decide where to place
the ambulances to maximize total coverage. Total coverage is defined as the sum of the coverages
of the individual zones, i.e. the number of people that can be reached by at least one ambulance
within eight minutes.

Since ambulance placements are assumed to be in the center of zones, putting two ambulances in the same
zone does not increase coverage. Therefore, ambulances should be placed in different zones to maximize
coverage.

Under the given conditions, we can easily find the optimal ambulance placement using a brute force
method: trying all $\binom{6}{3}$ choices of ambulance placements, and picking the one with the highest total coverage.
However, this solution is not scalable to larger cities, as the brute force method has time complexity
$O(n) = nk\binom{n}{k}$ where $n$ is the number of zones to cover, and $k$ is the number of ambulances to place, which
becomes intractable as $n$ and $k$ increase (since it has to check $\binom{n}{k}$ placements,
and calculating the total coverage of each placement requires $nk$ computations, summing the $k$ zone-zone
coverages for each of the $n$ ambulances). Quadrupling the size of the city
increases the computations required by a factor of 2 million (assuming the average zone size stays the same,
and the number of ambulances increases proportionally).

Therefore, a more scalable solution is needed. We discovered that a greedy heuristic also gives a good solution,
except with a much lower time complexity of $O(n) = n^2k$.
